### 2015-06-16 writing/S'15 LSTM/intro.tex
Final clarifications.

Our results engage with those of \newcite{vinyals2014grammar} and \newcite{dyer2015transition}, who find that sequence models can learn to recognize syntactic structure in natural language, at least when trained on explicitly syntactic tasks. The simplest model presented in Vinyals et al.~uses an LSTM sequence model to encode each sentence as a vector, and then generates a linearized parse (a sequence of brackets and constituent labels) with high accuracy using only the information present in the vector. This shows that the LSTM was able to identify the correct syntactic structures and also hints that it was able to develop a generalizable method for encoding these structures in vectors. However, the massive size of the dataset needed to train the model---250M tokens---leaves open the possibility that it primarily learned to generate only tree structures that it had already seen, representing them as simple hashes---which would not capture unseen tree structures---rather than as structured objects.
Our experiments, though, show that LSTMs can learn to understand tree structures when given enough data, suggesting that there is no fundamental obstacle to this kind of generalization.

>>>>

Our results engage with those of \newcite{vinyals2014grammar} and \newcite{dyer2015transition}, who find that sequence models can learn to recognize syntactic structure in natural language, at least when trained on explicitly syntactic tasks. The simplest model presented in Vinyals et al.~uses an LSTM sequence model to encode each sentence as a vector, and then generates a linearized parse (a sequence of brackets and constituent labels) with high accuracy using only the information present in the vector. This shows that the LSTM is able to identify the correct syntactic structures and also hints that it is able to develop a generalizable method for encoding these structures in vectors. However, the massive size of the dataset needed to train the model---250M tokens---leaves open the possibility that it primarily learns to generate only tree structures that it has already seen, representing them as simple hashes---which would not capture unseen tree structures---rather than as structured objects.
Our experiments, though, show that LSTMs can learn to understand tree structures when given enough data, suggesting that there is no fundamental obstacle to learning this kind of structured representation.

### 2015-06-16 writing/S'15 LSTM/methods.tex
Final clarifications.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.04\textwidth}
      \includegraphics[height=1.5in]{scale.pdf}
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
  \includegraphics[height=1.5in]{fig3c.pdf}
  \caption{Training on sz. $\le$3.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
    \includegraphics[height=1.5in]{fig4c.pdf}
  \caption{Training on sz. $\le$4.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
      \includegraphics[height=1.5in]{fig6c.pdf}
  \caption{Training on sz. $\le$6.}
\end{subfigure}~~
\begin{subfigure}[t]{0.08\textwidth}
      \includegraphics[height=1.5in]{leg.pdf}
\end{subfigure}
  \caption{Test accuracy on three experiments with increasingly rich training sets. The horizontal axis on each graph divides the test set expression pairs into bins by the number of logical operators in the more complex of the two expressions in the pair. The dotted line shows the size we trained on up to.}
  \label{prop-results} 
\end{figure*}

@@

\paragraph{Sentence models}
The sentence encoding component of the model transforms the (jointly learned) embeddings of the input words into a single sentence vector. We experiment with tree models (Figure~\ref{fig:model:tree}) with TreeRNN (eqn.~\ref{TreeRNN}), TreeRNTN (eqn.~\ref{TreeRNTN}), and TreeLSTM \cite{tai2015improved} activation functions. In addition, we use a sequence model (Figure~\ref{fig:model:seq}) with an LSTM activation function \cite{hochreiter1997long} implemented as in \newcite{zaremba2015recurrent}. Experiments with simpler non-LSTM RNN sequence models tended to underfit the training data, and are not included here.

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.04\textwidth}
      \includegraphics[height=1.5in]{scale.pdf}
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
  \includegraphics[height=1.5in]{fig3c.pdf}
  \caption{Training on sz. $\le$3.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
    \includegraphics[height=1.5in]{fig4c.pdf}
  \caption{Training on sz. $\le$4.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
      \includegraphics[height=1.5in]{fig6c.pdf}
  \caption{Training on sz. $\le$6.}
\end{subfigure}~~
\begin{subfigure}[t]{0.08\textwidth}
      \includegraphics[height=1.5in]{leg.pdf}
\end{subfigure}
  \caption{Test accuracy on three experiments with increasingly rich training sets. The horizontal axis on each graph divides the test set expression pairs into bins by the number of logical operators in the more complex of the two expressions in the pair. The dotted line shows the maximum size in each training set.}
  \label{prop-results} 
\end{figure*}

@@

\paragraph{Sentence models}
The sentence encoding component of the model transforms the (jointly learned) embeddings of the input words into a single sentence vector. We experiment with tree models (Figure~\ref{fig:model:tree}) with TreeRNN (eqn.~\ref{TreeRNN}), TreeRNTN (eqn.~\ref{TreeRNTN}), and TreeLSTM \cite{tai2015improved} activation functions. In addition, we use a sequence model (Figure~\ref{fig:model:seq}) with an LSTM activation function \cite{hochreiter1997long} implemented as in \newcite{zaremba2015recurrent}. Experiments with simpler non-LSTM RNN sequence models tended to badly underfit the training data, and are not included here.
